### 2014-06-30 Quality_Reports/PCR_bottleneck.Rmd
Loading data generated by PCR_bottleneck.R

# PCR bottleneck report

## PCR bottleneck

@@

```{r init,include = TRUE,echo = TRUE}
library(parallel)
library(GenomicAlignments)
library(ggplot2)
dr ="/NO_BACKUP/KelesGroup_DongjunChung/ChIP-exo/Landick_ChIP-exo3/rawdata"
folder = c("ChIPexo","ChIPseq_PET","ChIPseq_SET")
files = lapply(folder,function(x,dr){
  ff = list.files(file.path(dr,x))
  return(ff[!grepl("bai",ff) & !grepl("sam",ff)])},dr)
names(files) = folder
message(files[[1]])
```

For that purpose the following function was coded:

```{r PBC_fun,include = TRUE,results = "hide"}
PBC <- function(file)
{
  require(GenomicAlignments)
  message(file)
  rr = readGAlignmentsFromBam(file,param = NULL)
  ss1 = subset(rr,subset =strand(rr)=="+")
  ss2 = subset(rr,subset = strand(rr)=="-")
  N11 = length(unique(start(ss1)))
  N12 = length(unique(end(ss2)))
  N1 = N11+N12
  Nd1 = length(ss1)
  Nd2 = length(ss2)
  Nd = Nd1 + Nd2
  PBC1 = N11 / Nd1
  PBC2 = N12 / Nd2
  PBC = N1 /Nd
  message("PBC +:",round(PBC1,4))
  message("PBC -:",round(PBC2,4))
  message("PBC:",round(PBC,4))
  return(c(PBC_plus=PBC1,PBC_minus=PBC2,PBC=PBC))
}
```

>>>>

## PCR bottleneck report

### PCR bottleneck

@@

```{r init,include = FALSE,echo = TRUE,results = "hide"}
library(parallel)
library(GenomicAlignments)
library(ggplot2)
dr ="/NO_BACKUP/KelesGroup_DongjunChung/ChIP-exo/Landick_ChIP-exo3/rawdata"
folder = c("ChIPexo","ChIPseq_PET","ChIPseq_SET")
files = lapply(folder,function(x,dr){
  ff = list.files(file.path(dr,x))
  return(ff[!grepl("bai",ff) & !grepl("sam",ff)])},dr)
names(files) = folder
```
### Code

The following function was used to calculate the PBC:

```{r PBC_fun,include = TRUE,results = "hide",echo = TRUE}
PBC <- function(file)
{
  require(GenomicAlignments)
  rr = readGAlignmentsFromBam(file,param = NULL)
  ss1 = subset(rr,subset =strand(rr)=="+")
  ss2 = subset(rr,subset = strand(rr)=="-")
  N11 = length(unique(start(ss1)))
  N12 = length(unique(end(ss2)))
  N1 = N11+N12
  Nd1 = length(ss1)
  Nd2 = length(ss2)
  Nd = Nd1 + Nd2
  PBC1 = round(N11 / Nd1,4)
  PBC2 = round(N12 / Nd2,4)
  PBC = round(N1 /Nd,4)
  return(c(PBC_plus=PBC1,PBC_minus=PBC2,PBC=PBC))  
}
```
And the following results where obtained:
```{r load_data,include = FALSE,echo = TRUE,results = "hide"}
load("../RData/PBC.RData")
```

```{r show,include = TRUE,echo = TRUE, results = "asis"}
ls()
```
